Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
rw

\Rui{this sentence does not belong to rw (We suspect...)-->} We
suspect that several highly suspicious components—often involved in failing, but
seldom in passing test runs—may be unrelated to the bug.

Prior work has investigated the \ds{}-\sfl{}
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
Overall, these studies reported promissing results but based their conclusions
on a very small group of (mostly artificial) faults and using different
techniques.

\Rui{not related work. more of motivation (avoid words such as believe)-->}
Although, \ds{} does not ensure the improvement of \sfl{} since it
can remove faulty statements from the failing test, we believe it has a great
potential to help reducing test cases and improve \sfl{} accuracy. In this
study, a larger set of faults is evaluated and a more rigorous experimental
methodology.

>>>>

Prior work has investigated the \ds{}-\sfl{}
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
Overall, these studies reported promissing results but based their conclusions
on a very small group of (mostly artificial) faults and using different
techniques. In this
study, a larger set of faults is evaluated and a more rigorous experimental
methodology.
In contrast with other studies on this combination,
our approach is the first using Critical Slicing to minimize test cases
and leveraging \sfl{} rank to choose and minimize the top-$k$ of
highest-ranked faulty classes.
